\section{Introduction} % (fold)
\label{sec:Introduction}

A common challenge in computer vision is accurately tracking features through a
video.
%Many computer vision algorithms build upon these tracked features, so
%accurately tracking the features and understanding the traces through time that
%the features produce is important.  
There has been much prior work on feature
selection (ie SIFT \cite{sift}), which focuses on finding features in an image
and picking out the ``best'' ones.  Important later work focused on matching
features between images and after that tracking features through a sequence of
frames in a video (ie KLT \cite{klt}).  
%These tools produce a trace of the features through space and time.
%Given these feature traces, researchers attempt to use them for
%numerous computer vision applications
Researchers have used such feature traces for numerous applications; we focus
on two: robust structure from motion and robust movement isolation.    

Structure from motion is a common application in which we attempt to recover
the structure of the objects in a scene based on the feature traces.  However,
incorrect feature traces worsen the results of the structure from motion
algorithm.  This became more problematic as SIFT and KLT had some difficulty
with shaky video, such as that produced from waving a mobile phone around.
We found that traces from moving objects in a scene also weakened the
results of the structure from motion algorithm.  Therefore, we sought to create
a model by which to separate these abnormal feature traces from the normal,
valid ones, with the ultimate goal of removing abnormal traces and improving
the structure from motion.  Our key insight, which we will explain in more
detail later, is that normal traces of static objects in a scene generally look
similar to one another since their trace is almost entirely based on the motion
of the camera, where as the bad traces and traces of moving objects look very
different.  Therefore, we created a model to compare trace shapes and detect
outliers.

As we produced this model, we found it was excellent at detecting moving
objects in a scene, regardless of camera motion.  We decided to apply our
outlier detection model to robustly isolating motion in shaky video.  Given an
``outlier score'' from our previous model we create a secondary model to
estimate if a given pixel in a given frame of video is of a moving object or a
static object, based on the traces around that pixel and their scores.  With
this model we can construct a video containing only the moving elements in the
video and removing background pixels.

In Section \ref{sec:background} we give a brief background on the computer
vision research that we build upon, such as SIFT, KLT, and structure from
motion.  In Section \ref{sec:formulation} we more precisely formulate the
problem and describe our model for outlier detection.  In Section \ref{sec:sfm}
we describe the application of our model to the problem of robust structure
from motion, and in Section \ref{sec:motion} we describe the application of our
model to the problem of robust motion isolation.  For each application we run
our algorithm on numerous videos, some taken by us with mobile phones and
others downloaded from YouTube, and analyze the results.
